\documentclass[12pt, a4paper]{article}

\usepackage[english]{babel}
\usepackage{booktabs} 
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{
	colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}


\title{\textcolor{blue}{The Tasks for Data Analyst Intership by Rambler Group}}
\date{03-13-2020}
\author{Aleksandr Kasian}

\begin{document}

\begin{titlepage}
	\maketitle
	\pagenumbering{gobble}
\end{titlepage}
\pagenumbering{arabic}
\newpage

\tableofcontents

\newpage

\section*{Description}
\addcontentsline{toc}{section}{\protect\numberline{}Description}%
The tasks in the following document were represented by Rambler Group to the role "the Data Analyst Internship".

\section*{Problem 1}
\addcontentsline{toc}{section}{\protect\numberline{}Problem 1}%
Rambler Group's advertising campaign uses most fascinating and most memorable banners.
Analytics have access to the databases containing data regard the banner' showing.
The \textbf{Shows\_table} contains:
\begin{itemize}
	\item \emph{show\_id} - an identifier of a showing 
	\item \emph{day} - a day of a showig
\end{itemize}

\begin{table}[h]
	\begin{tabular}{|l|l|}
	\hline
	show\_id & day        \\ \hline
	12367    & 2018-10-04 \\ \hline
	28736    & 2019-02-22 \\ \hline
	19862    & 2019-01-31 \\ \hline
	\end{tabular}
\end{table}

\noindent
The \textbf{Click\_table} contains:
\begin{itemize}
	\item \emph{click\_id} - a show identifier clicked by an user
	\item \emph{bounce} - an user dismissing from an advertising after click (0 - when an user relinked to the site 
	he keened in the information on the site. 1 - an user immediatly left the site.)
\end{itemize}

\begin{table}[h]
	\begin{tabular}{|l|l|}
		\hline
		click\_id & bounce	\\ \hline
		12367 	  & 1       \\ \hline
		15627 	  & 0       \\ \hline
		28735     & 0		\\ \hline	
	\end{tabular}
\end{table}

\noindent
You need to get all users who clicked at a banner in February 2020, and 
they din't reject an advertising.

\newpage
\section*{Problem 2}
\addcontentsline{toc}{section}{\protect\numberline{}Problem 2}%

\noindent
The friendly Rambler Group's community likes to play in the table football: 
At the odd days they play before lunch, at the even days the play after lunch.
They are splitting at the N teams among each other, and every team plays with each another team.
Because of the splitting onto the teams is randomly, the product of the games is random.
Also I would note that there are no ties. Only win or lose.
\begin{enumerate}
	\item Estimate the probability if one of the teams will finish the tournament without defeat.
	\item How many times do you need to hold a tournament, so that with a probability of 98\% at least once this happened?
\end{enumerate} 
\end{document}